The \dealii{} Library, Version 9.3

### 2021-06-21 9.3/paper.tex
Fix another minor mistake.
Only DoFHandler iterators have get_fe().

The introduction of simplex and mixed meshes leads to some implications
for the user if these features are to be used. For instance, each cell might have a different type with
different number of vertices, lines, and faces so that these quantities can not be
compile-time constants anymore. This information used to be queried from
the \texttt{GeometryInfo} class. To avoid using this class, we have extended
relevant classes, e.g., \texttt{TriaAccessor} or \texttt{TriaCellAccessor},
with useful new functions like \texttt{n\_vertices()}, \texttt{n\_lines()}, or
\texttt{n\_faces()} so that users can simply write:
\begin{c++}
for (const auto &cell : tria.active_cell_iterators())
  for (unsigned int f = 0; f < cell->n_faces(); ++f)
    // do something with cell->face(f);
\end{c++}
Alternatively, one can use an iterator-based approach to loop over all faces
of a cell, introduced in the previous release. The relevant functions have been adjusted to be able to deal with
the now variable number of faces per cell:
\begin{c++}
for (const auto &cell : tria.active_cell_iterators())
  for (const auto &face : cell->face_iterators())
    // do something with face
\end{c++}
Furthermore, for mixed meshes, the number of degrees of freedom will differ between cells so that
cell-local arrays need to be resized for each
cell (as has previously already been the case in the $hp$-context):
\begin{c++}
std::vector<double> local_rhs;
for (const auto &cell : tria.active_cell_iterators())
 {
   hp_fe_values.reinit(cell);
   local_rhs.resize(cell->get_fe().n_dofs_per_cell());
 }
\end{c++}

>>>>

The introduction of simplex and mixed meshes leads to some implications
for the user if these features are to be used. For instance, each cell might have a different type with
different number of vertices, lines, and faces so that these quantities can not be
compile-time constants anymore. This information used to be queried from
the \texttt{GeometryInfo} class. To avoid using this class, we have extended
relevant classes, e.g., \texttt{TriaAccessor} or \texttt{TriaCellAccessor},
with useful new functions like \texttt{n\_vertices()}, \texttt{n\_lines()}, or
\texttt{n\_faces()} so that users can simply write:
\begin{c++}
for (const auto &cell : tria.active_cell_iterators())
  for (unsigned int f = 0; f < cell->n_faces(); ++f)
    // do something with cell->face(f);
\end{c++}
Alternatively, one can use an iterator-based approach to loop over all faces
of a cell, introduced in the previous release. The relevant functions have been adjusted to be able to deal with
the now variable number of faces per cell:
\begin{c++}
for (const auto &cell : tria.active_cell_iterators())
  for (const auto &face : cell->face_iterators())
    // do something with face
\end{c++}
Furthermore, for mixed meshes, the number of degrees of freedom will differ between cells so that
cell-local arrays need to be resized for each
cell (as has previously already been the case in the $hp$-context):
\begin{c++}
std::vector<double> local_rhs;
for (const auto &cell : dof_handler.active_cell_iterators())
 {
   hp_fe_values.reinit(cell);
   local_rhs.resize(cell->get_fe().n_dofs_per_cell());
 }
\end{c++}
